---
title: "Old Faithful Analysis"
author: "Phil Dean"
date: "28/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is an example analysis for the 'Robust and Open Analysis in R' workshop. 

We shall be exploring the 'Old Faithful' dataset from Base R. 

# Import and save data

First we import the data from the datasets package. 
```{r}
df <- datasets::faithful
```

We can now save this in the `data` folder as a `csv` for maximum interoptability. 

```{r}
readr::write_csv(x=df, path='data/old_faithfull.csv')
```

# Plot marginal distributions
We can plot  marginal distirbution for each variable. 

```{r}
hist(df$eruptions)
hist(df$waiting)
```

We can save them as normal as well: 
```{r}
png(filename='images/eruption_density.png')
hist(df$eruptions)
dev.off()
png(filename='images/waiting_density.png')
hist(df$waiting)
dev.off()
```

Interesting!  Both distributions seem to be bimodal, let's look at the scatter of one against the other. 

```{r}
plot(df$waiting, df$eruptions)
```

Clearly we have that Old Faithful has two 'modes' - waiting for a short time with small eruprtions
and waiting for a longer time with larger erutions. 